### 2015-05-15 conclusion.tex
openvpn stuff etc

\chapter{Conclusion}

@@

\paragraph{Registering public key verification with the crypto API}
As we saw in \ref{sec:section-with-RSA-BA414}, the driver is already capable of offloading a large portion of public key operations to the IP, but only with very specific libraries at the time being -- openSSL in our case.
The next step is to register the very same operations with the crypto API so it can be used without having to rely on a custom openSSL engine.

>>>>

\chapter{Discussion and conclusion}

@@

\paragraph{Registering public key verification with the crypto API}
As we saw in \ref{sec:section-with-RSA-BA414}, the driver is already capable of offloading a large portion of public key operations to the IP, but only with very specific libraries at the time being -- openSSL in our case.
The next step is to register the very same operations with the crypto API so it can be used without having to rely on a custom openSSL engine.
This feature would require to work very closely to the linux kernel developpement.
Indeed, if the signature verification using public key cryptography has been available in the kernel since 2013, a public key encryption API has only been introduced in late April 2015~\cite{cyrpto-api-pk-encryption} and is still under request for comments.

### 2015-05-15 presentation.tex
openvpn stuff etc

\section{Experimental setup}
The experimental environment is build around a standard x86 host and an ARM Cortex-A9 alongside an Altera Cyclone V FPGA as the target.

\subsection{x86 host}

\begin{framed}
\begin{description}
	\item[OS] Ubuntu 12.04 LTS, kernel 3.16
	\item[CPU] Intel Core-i3 ... (two logical core out of four)
	\item[RAM] 1.5GB DDR3
\end{description}
\end{framed}

@@

>>>>

\section{Experimental setup}
The experimental environment is built around a standard x86 host and an ARM Cortex-A9 alongside an Altera Cyclone V FPGA as the target.
Both are linked toghether through a network capped by 100Mbps switches.
Both stations have gigabits ethernet interface and could hence be diretly connected to each other, but in that case the communication would be limited by the I/O transfers of the storage units -- a hard drive disk in one case, an micro-SD card in the second -- on which we can not depend to set a constant throughput limitation, as it is highly influenced by the data block size and general health of the support.

\subsection{x86 host}
The desktop host runs on Windows 7 Professional 64-bit, but a virtual machine using a Linux distribution is used for the developpement and testings.

\begin{framed}
\begin{description}
	\item[OS] Ubuntu 12.04 LTS, kernel 3.16
	\item[CPU] Intel Core-i3 ... (two logical core out of four)
	\item[RAM] 1GB DDR3
\end{description}
\end{framed}

@@

\subsection{ARM DS-5 Streamline}
% Use a daemon and a driver to get system info and send them to another machine. Has almost no impact on the performance and the load of the system.

\subsection{Barco Silex' IPs}
% table with the BA411E and BA414E showing the respective operations and crypto alg
